The influence of resource use on yield versus sale price trade-off in Australian vineyards

### 2023-11-20 article.tex
ship it

\begin{document}
\begin{linenumbers}
\begin{frontmatter}
%% Title, authors and addresses
%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \affiliation for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \affiliation{organization={},
%%            addressline={}, 
%%            city={},
%%            postcode={}, 
%%            state={},
%%            country={}}
%% \fntext[label3]{}
\title{The influence of resource use on yield versus sale price trade-off in Australian vineyards}
%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \affiliation[label1]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%%
%% \affiliation[label2]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%\affiliation[label1]{organization={QUT},
%  addressline={},
%  city={},
%  postcode={},
%  state={QLD},
%  country={}}
%\affiliation[label2]{organization={AWRI},
%  addressline={},
%  city={},
%  postcode={},
%  state={SA},
%  country={}}
%\affiliation[label3]{organization={Food Agility CRC},
%  addressline={},
%  city={},
%  postcode={},
%  state={Vic},
%  country={}}
\author[label1,label2,label3]{Author}
\date{02/08/2023}
\begin{abstract}
% The word limit needs to be checked.
When strategies for a sustainable winegrowing industry are assessed, there is a trade-off between balancing the amount of resources invested and the resultant yield and sale price of the produce. In this analysis we observe relationships between resource use, yield and sale price through the use of statistical models. The dataset used for this analysis includes data collected for the past 10 years from 1261 vineyards located over a diverse range of Australian winegrowing regions. Yield and sale price was modelled to resource factors related to water use and Green House Gas (GHG) emissions. The analysis confirmed a strong relationship between area and resource use, with the overall area of a vineyard and its access to resources greatly determining the upper limit of yield. However, area was also negatively related to the average sale price of grapes, we find that higher average sale prices were connected to high resource inputs per area; rather than to the overall expenditure of resources. Regional and temporal effects on vineyard yield and average sales price were also identified. Overall, the analysis highlighted the importance of considering a vineyard's business goal, region, external pressures and economies of scale, when considering whether to pursue higher yields or average sales prices.
\end{abstract}
%%Graphical abstract`
%\begin{graphicalabstract}
 % \includegraphics{graphical_abstract.jpeg}
%\end{graphicalabstract}'

@@

\section{Introduction}
The global focus on sustainability in agronomic industries has changed the way in which these enterprises do business. A dilemma exists across agriculture through shared fundamental considerations of resource use such as water and fuel, and the resultant yield and crop value that is produced\citep{hemmingCherryTomatoProduction2020,kawasakiQualityMattersMore2016, zhuEffectsNitrogenLevel2017}. The average price of grapes for wine production is driven through its integration within the wine industry. An important connection between grapes and their price is the grapes perceived quality, which initially defines a wines potential through the grapes chemical makeup \citep{blackTerpenoidsTheirRole2015,schreierFlavorCompositionWines1979}. Grapes of higher of perceived quality or grapes from particularly famous regions are likely to have higher prices \citep{wineaustraliaNationalVintageReport2021}.  Grape quality is connected to the market value of winegrapes, with Wine Australia explicitly defining grape quality through the use of discrete price brackets in their annual reports \citep{winemakersfederationofaustraliaNationalVintageReport2018}. Although it is also important to note that the generalisation made to reflect quality through using average price assumes a due diligence of those who purchasing the grapes \citep{yeggeInfluenceSensoryNonsensory2001}. The economic sustainability of a vineyard is tied to this market culture driven by the wine industry. The consideration of sustainability within viticulture is also subject to environmental and socio-demographic pressures \citep{santiago-brownSustainabilityAssessmentWineGrape2015}. In the Australian context, these pressures include biosecurity and climate and international market changes \citep{canadellMultidecadalIncreaseForest2021,longbottomRoleVineyardPractices2015,oliverReviewSoilPhysical2013}.
\par
There is an extensive amount of research into the varied effects of factors on grape quality and yield \citep{heFruitYieldPrediction2022,laurentLocalInfluenceClimate2022,liakosMachineLearningAgriculture2018}. With there being a lack of research on grape sale price and its driving factors due to the lack of long-term and in-depth data. Furthermore, individual factors are often studied in isolation with yield and sales price not appearing together \citep{abbalDecisionSupportSystem2016}. The lack of consolidated datasets restricts the ability to gain statistical insights at large scales and across multiple regions, as a result broader studies are lacking \citep{keithjonesAustralianWineIndustry2002,knightFirmResourcesDevelopment2019}. The dataset used for this analysis includes data spanning 10 years from a multitude of vineyards located over a diverse range of Australian winegrowing regions. We use this dataset to describe the relationship of resources related to water and fuel use with the output yield and average sale price of the resultant product, taking into account the size and location of the vineyard. The practical addition of this aim is a baseline for comparison: given a vineyard within Australia, one could estimate the comparative efficiency with regard to the tradeoff between invested resources, yield and average sale price. This is the first time that such a trade off has been confirmed explicitly across such varying regions, scales and climates in the Australian winegrowing industry.
\section{Methods}
\subsection{Data}

@@

Data used in these analyses were obtained from Sustainable Winegrowing Australia and Wine Australia. Sustainable Winegrowing Australia is Australia's national wine industry sustainability program, which aims to facilitate grape-growers and winemakers in demonstrating and improving their sustainability \citep{swaSustainableWingrowingAustralia2022}. Data collected by Sustainable Winegrowing Australia is entered voluntarily by winegrowers at the end of harvest. Wine Australia is an Australian Government statutory authority governed by the Wine Australia Act \citep{attorney-generalsdepartmentWineAustraliaCorporation2010}. Data collected by Wine Australia is publicly available.

@@

Predicted variables in this analysis were yield, defined as the total tonnes of grapes harvested, and average sale price of grapes. Both response variables were examined as totals and as scales of area harvested. Values were compared in this manner to observe how economies of scale affect the use of resources.

@@

Data obtained from Wine Australia were collected via phone surveys and included: total tonnes purchased, average price per tonne and yearly change in price for region and grape varietal. Data recorded by Sustainable Winegrowing Australia was entered manually by winegrowers using a web based interface with some fields being optional. Required variables included: region, harvest year, yield and area harvested. Harvest year and region were recorded as categorical variables. Optional variables included average sale price, water used and fuel used (diesel, petrol, biodiesel and LPG). The dataset was limited to respondents that recorded values for area harvested, water used, yield and fuel use. To enable direct comparisons between fuels, fuel use was converted to tonnes of Carbon Dioxide equivalent and collectively referenced to as emissions.
Average sale price was an optional field in the Sustainable Winegrowing Australia's dataset. Missing values were improved using regional average prices from Wine Australia. Two subsets of data were then created for the analysis. The first subset contained all vineyards and was used for two models (Model 1 and Model 2, see Table \ref{tab:tab1}). The second subset contained vineyards which either recorded a value for average price of sale per tonne through Sustainable Winegrowing Australia, or were within a region with an average price of sale recorded by Wine Australia; this subset was used for three further models (Models 3, 4 and 5, see Table \ref{tab:tab1}). These subsets meant that the data would be limited to samples which had recorded values for the response variables (see Table \ref{tab:tab1}), where every sample had a recorded value for yield but not average price of sale per tonne.

@@

The second subset of data (used for Model 3, Model 4 and Model 5, see Table \ref{tab:tab1}) contained 2878 samples spanning the period from 2015 to 2022, covering 51 GI Regions and 944 separate vineyards.Average price of sale per tonne was extracted from both Wine Australia (1842 values) and Sustainable Winegrowing Australia (remaining 1036 values).

@@

We converted multiple emission sources into scope one emissions using the equation given from the Australian National Greenhouse Accounts Factors \citep{agdeeNationalGreenhouseAccounts2021}, shown as

@@

was used to convert the quantity of fuel in litres, $Q$, using a prescribed Energy Content, $EC$, and emission factors of scope one, $EF1$, and scope three, $EF3$, to tonnes of Carbon Dioxide Emission equivalent, $tCO2e$ \citep{departmentofclimatechangeenergytheenvironmentandwaterAustralianNationalGreenhouse2022}.

@@

\begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{my_map.pdf}}
  \caption{Map of each GI Regions average income for a vineyard of that region (average grape sale price per tonne $\times$ total tonnes yielded).}\label{fig:map}
\end{figure}%%

@@

The site of a vineyard predetermines several physical parameters such as climate, geology and soil, making location a widely considered key determinant of grape yield and average sale price \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,fragaMultivariateClusteringViticultural2017}. Differences in vineyard locations were captured through the use of Geographical Indicator Regions (GI Regions, see Figure \ref{fig:map}) defined by Wine Australia \citep{hallidayAustralianWineEncyclopedia2009,oliverReviewSoilPhysical2013,soarClimateDriversRed2008}. Each GI Region has its own unique mixture of climatic and geophysical properties that describes a unique winegrowing region within Australia and is a protected trademark under the Wine Australia act \citep{attorney-generalsdepartmentWineAustraliaCorporation2010}. Both Wine Australia and Sustainable Winegrowing Australia used the same GI Region categorical variable format to describe location.

@@

Models were validated using K-fold cross validation calculated. K-fold cross validation works by removing a subset of data from the sample used to train models and then predicts those variables to determine how sensitive the model is to changes in the sample data . For this analysis each model was validated using 10 folds, repeated 100 times.

@@

\begin{table}[]
  \caption{Summary of each Models coefficients for continuous variables}\label{tab:contvar}
  \resizebox{\textwidth}{!}{
    \begin{tabular}{@{}cccccccc@{}}
      \begin{tabular}{@{}cccccccc@{}}
        \toprule
        \textbf{} & \textbf{} & \textbf{Intercept} & \textbf{Area Harvested} & \textbf{Water Used} & \textbf{\begin{tabular}[c]{@{}c@{}}Scope One\\ Emissions\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Area Harvested \\ *\\ Scope One Emissions\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Area Harvested \\ * \\ Water Used\end{tabular}} \\ \midrule
        \multirow{2}{*}{Model 1} & Coefficient & -0.0332 & 0.7418 & 0.0866 & 0.0673 &  &  \\
         & Std Error & 0.0196 & 0.0100 & 0.0089 & 0.0080 &  &  \\
         &  &  &  &  &  &  &  \\
         \multirow{2}{*}{Model 2} & Coefficient & 0.1696 & 0.5774 & 0.1079 & 0.0850 & -0.0497 & -0.0535 \\
         & Std Error & 0.0591 & 0.0148 & 0.0131 & 0.0117 & 0.0081 & 0.0084 \\
         &  &  &  &  &  &  &  \\
         \multirow{2}{*}{Model 3} & Coefficient & 0.0181 & 0.9713 & -0.0231 & -0.0070 &  &  \\
         & Std Error & 0.0130 & 0.0072 & 0.0069 & 0.0057 &  &  \\
         &  &  &  &  &  &  &  \\
         \multirow{2}{*}{Model 4} & Coefficient & 0.1450 & 0.0024 & -0.0466 & -0.0170 & 0.0115 & 0.0014 \\
         & Std Error & 0.0528 & 0.0150 & 0.0143 & 0.0118 & 0.0079 & 0.0083 \\
         &  &  &  &  &  &  &  \\
         \multirow{2}{*}{Model 5} & Coefficient & 0.1517 &  & -0.0404 & -0.0171 &  &  \\
         & Std Error & 0.0527 &  & 0.0113 & 0.0097 &  &  \\ \bottomrule
        \end{tabular}

@@

The regression coefficients for the year for each model is depicted in Figure \ref{fig:yearly}. The first year for a model's data is used as the baseline. The Adelaide Hills is used as the regional baseline with the interaction between year and region using the first year and the Adelaide Hills as the baseline. Region and year contributed, in some but not all cases, more than the other variables. However, some years are not significant, as they are not statistically different from 0, given their error. Models 4 and 5 are very similar, indicating that the exclusion of area does not greatly affect the contribution from yearly influence. Models 4 and 5 have the most prominent trends, showing an increase in yearly effects over time, with Model 3 also increasing from 2016 to 2018 but plateau afterwards. Models 1 and 2 do not show a clear trend but do drop during 2017 and 2018 after increasing in the first 3 years.
\par
\begin{figure}
  \includegraphics{yearly_plots.pdf}
  \caption{Model Coefficient values for Year, with standard error bars.}\label{fig:yearly}
  \end{figure}

@@

Regional differences are summarised in Figure \ref{fig:spider}. The most notable difference is between vineyards within 'Hot' and 'Very Dry' regions (warm inland regions), where high average sale prices are historically low, and yield is high. Water Use changes dramatically between these regions as well, with water being a driving force for yield but not necessarily average sale price. The warmer and drier regions tend to also have larger vineyards.
\par
\begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{starplots.png}}
  \caption{Radar plot of climatic profile's resource use, yield and average sale price. The left reflects vineyards in different climatic temperatures. The right reflects vineyards in different rainfall climates.}\label{fig:spider}
\end{figure}

@@

There was an expected strong relationship between size and resource use, with the overall area of a vineyard and its access to resources greatly determining the upper limit of potential yield. However, size was also inversely related to the potential average sale price, with higher sales prices being related to high resource inputs per area; rather than to the overall expenditure of resources. Vineyard yields and sales price changed greatly by region and year. Even given regional and yearly changes, there was a strong connection between smaller vineyards and higher sales prices. This could have been due to more attention available when managing smaller properties.

@@

The lack of significance of scope one emissions and its contribution to models, given its F-statistics, could be indicative that other vineyard activities requiring fuel are not leading factors for a vineyards avereage sale price. The relationship between yield, value and area was not simply about efficiently producing the most grapes. It is possible that the relationship of scope one emissions between yield and sale price was closely tied to a vineyard's area due to requiring more fuel to address more issues over greater distances. It is difficult to discern the connection of scope one emissions directly, as fuel can be used for a broad category of activities. 

@@

There are many on-the-ground decisions that influence both sales price and yield. The decision to prioritise average sale price over quantity, is governed by complex physical and social forces, for example international market demands, disease pressures and natural disasters \citep{abadCoverCropsViticulture2021,cortezUsingDataMining2009,hallWithinseasonTemporalVariation2011,i.goodwinManagingSoilWater2009,kasimatiPredictingGrapeSugar2022,oliverReviewSoilPhysical2013,srivastavaNondestructiveSensingMethods2018}, with many of these occurrences being highlighted throughout the reports from Wine Australia \citep{wineaustraliaNationalVintageReport2019,wineaustraliaNationalVintageReport2021,wineaustraliaNationalVintageReport2022,winemakersfederationofaustraliaNationalVintageReport2013,winemakersfederationofaustraliaNationalVintageReport2014,winemakersfederationofaustraliaNationalVintageReport2015,winemakersfederationofaustraliaNationalVintageReport2016,winemakersfederationofaustraliaNationalVintageReport2017,winemakersfederationofaustraliaNationalVintageReport2018} over the past decade. However, the changes in the coefficients (see Figure \ref{fig:yearly}) are not reflective of many known occurrences, such as the 2020 bush fires, which had higher values for coefficients than prior years; During the 2020 bush fires 40,000 tonnes of grapes were lost across 18 different wine regions due to bush fires and smoke taint. In comparison to countrywide pressures such as drought, this damage made up only 3\% of the total amount of grapes for that year; although acknowledged as a considerable loss on an individual basis, it was deemed to be only a minor national concern by Wine Australia when compared to other environmental pressures such as drought \citep{wineaustraliaNationalVintageReport2020}

@@

Some regions appeared to produce grapes of lower average sale price at scale whilst others focussed on producing higher priced grapes in lower volumes. This empirical finding is consistent with Wine Australia's annual reports, which shows that some GI regions, such as the Riverland, are known for producing large amounts of lower grade (low value per tonne) grapes \citep{wineaustraliaNationalVintageReport2022,winemakersfederationofaustraliaNationalVintageReport2017}. Comparatively, other regions, such as Tasmania, only produce grapes of higher sales price but in smaller quantities. The difference in pricing per tonne between the lowest and highest graded grapes can be greater than a hundred times the difference in value per tonne. Not all regions target only one grade of grape, with some producing a variety of differently graded grapes; such as the Yarra Valley, which produces grades from C to A. This effect could stifle the potential for market opportunities within lesser known regions. A further possibility is the existence of regional upper limits on potential sales price, or that there are diminishing returns in some regions when pursuing higher sales prices or quantity; however these types of relationships may be obfuscated by knowledgeable winegrowers who avoid this pitfall.

@@

Due to regional differences, different strategies are also  employed across different regions, such as some regions targeting mass production over higher sales price. This is most notable when grouping regions by climate, especially when considering GI Regions in the 'Hot Very Dry' climate (see Figure \ref{fig:yield_vs_value_area}). 

>>>>

\begin{document}
\begin{linenumbers}
\begin{frontmatter}
%% Title, authors and addresses
%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \affiliation for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \affiliation{organization={},
%%            addressline={}, 
%%            city={},
%%            postcode={}, 
%%            state={},
%%            country={}}
%% \fntext[label3]{}
\title{The influence of resource use on yield versus sale price trade-off in Australian vineyards}
%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \affiliation[label1]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%%
%% \affiliation[label2]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%\affiliation[label1]{organization={QUT},
%  addressline={},
%  city={},
%  postcode={},
%  state={QLD},
%  country={}}
%\affiliation[label2]{organization={AWRI},
%  addressline={},
%  city={},
%  postcode={},
%  state={SA},
%  country={}}
%\affiliation[label3]{organization={Food Agility CRC},
%  addressline={},
%  city={},
%  postcode={},
%  state={Vic},
%  country={}}
\author[label1,label2,label3]{Author}
\date{02/08/2023}
\begin{abstract}
% The word limit needs to be checked.
When strategies for a sustainable winegrowing industry are assessed, there is a trade-off between balancing the amount of resources invested and the resultant yield and sale price of the produce. In this analysis we observe relationships between resource use, yield and sale price through the use of statistical models. The dataset used for this analysis includes data collected for the past 10 years from 1261 vineyards located over a diverse range of Australian winegrowing regions. Yield and sale price was modelled to the resource use factors water use and Green House Gas (GHG) emissions. The analysis confirmed a strong relationship between area and resource use, with the overall area of a vineyard and its access to resources greatly determining the upper limit of yield. However, area was also negatively related to the average sale price of grapes, we find that higher average sale prices were connected to high resource inputs per area; rather than to the overall expenditure of resources. Regional and temporal effects on vineyard yield and average sales price were also identified. Overall, the analysis highlighted the importance of considering a vineyard's business goal, region, external pressures and economies of scale, when considering whether to pursue higher yields or higher average sales prices.
\end{abstract}
%%Graphical abstract`
%\begin{graphicalabstract}
 % \includegraphics{graphical_abstract.jpeg}
%\end{graphicalabstract}'

@@

\section{Introduction}
The global focus on sustainability in agronomic industries has changed the way in which these enterprises do business. A dilemma exists across agriculture through shared fundamental considerations of resource use such as water and fuel, and the resultant yield and crop value that is produced\citep{hemmingCherryTomatoProduction2020,kawasakiQualityMattersMore2016, zhuEffectsNitrogenLevel2017}. The average price of grapes for wine production is driven through its integration within the wine industry. An important connection between grapes and their price is the grapes perceived quality, which initially defines a wines potential through the grapes chemical makeup \citep{blackTerpenoidsTheirRole2015,schreierFlavorCompositionWines1979}. Grapes of higher of perceived quality or grapes from particularly famous regions are likely to have higher prices \citep{wineaustraliaNationalVintageReport2021}.  Grape quality is connected to the market value of winegrapes, with Wine Australia explicitly defining grape quality through the use of discrete price brackets in their annual reports \citep{winemakersfederationofaustraliaNationalVintageReport2018}. Although it is also important to note that the generalisation made to reflect quality through using average price assumes a due diligence of those who purchasing the grapes \citep{yeggeInfluenceSensoryNonsensory2001}. The economic sustainability of a vineyard is tied to this market culture driven by the wine industry. The consideration of sustainability within viticulture is also subject to environmental and sociodemographic pressures \citep{santiago-brownSustainabilityAssessmentWineGrape2015}. In the Australian context, these pressures include biosecurity and climate and international market changes \citep{canadellMultidecadalIncreaseForest2021,longbottomRoleVineyardPractices2015,oliverReviewSoilPhysical2013}.
\par
There is an extensive amount of research into the varied effects of factors on grape quality and yield \citep{heFruitYieldPrediction2022,laurentLocalInfluenceClimate2022,liakosMachineLearningAgriculture2018}. With there being a lack of research on grape sale price and its driving factors due to the lack of long-term and in-depth data. Furthermore, individual factors are often studied in isolation with yield and sales price not appearing together \citep{abbalDecisionSupportSystem2016}. The lack of consolidated datasets restricts the ability to gain statistical insights at large scales and across multiple regions, as a result broader studies are lacking \citep{keithjonesAustralianWineIndustry2002,knightFirmResourcesDevelopment2019}. The dataset used for this analysis includes data spanning 10 years from a multitude of vineyards located over a diverse range of Australian winegrowing regions. We use this dataset to describe the relationship of resources related to water and fuel use with the output yield and average sale price of the resultant product, taking into account the size and location of the vineyard. The practical addition of this aim is a baseline for comparison: given a vineyard within Australia, one could estimate the comparative efficiency with regard to the trade-off between invested resources, yield and average sale price. This is the first time that such a trade-off has been confirmed explicitly across such varying regions, scales and climates in the Australian winegrowing industry.
\section{Methods}
\subsection{Data}

@@

Data used in these analyses were obtained from Sustainable Winegrowing Australia and Wine Australia. Sustainable Winegrowing Australia is Australia's national wine industry sustainability program, which aims to facilitate grape-growers and winemakers in demonstrating and improving their sustainability \citep{swaSustainableWingrowingAustralia2022}. Wine Australia is an Australian Government statutory authority governed by the Wine Australia Act \citep{attorney-generalsdepartmentWineAustraliaCorporation2010}. Data collected by Wine Australia is publicly available. The predicted variables in this analysis where yield, defined as the total tonnes of grapes harvested, and average sale price of grapes in Australian dollars per tonne. Both response variables were examined as totals and as scales of area harvested. Values were compared in this manner to observe how economies of scale affect the use of resources.
\par

Data recorded by Sustainable Winegrowing Australia was entered manually by winegrowers voluntarily using a web based interface. For each model, vineyards were only included if they recorded all the variables used for the corresponding model (see Table \ref{tab:modelsummary}). Each vineyard had at least recorded region, harvest year, yield and area harvested. Other variables that were used but not present for every single vineyard were average sale price, water used and fuel used (diesel, petrol, biodiesel and LPG). To enable direct comparisons between fuels, fuel use was converted to tonnes of Carbon Dioxide equivalent and collectively referenced to as emissions. All variables were continuous except for harvest year and region, which were categorical variables.

@@

As data from Sustainable Wine Australia was voluntarily given, missing values were improved using regional average prices from the Wine Australia data. Data obtained from Wine Australia were collected via phone surveys and included: total tonnes purchased, average price per tonne and yearly change in price for region and grape varietal; with the data being publicly available.

@@

As the models used similar variables the original data was only split into two distinct subsets that could be used across the different models. The first subset contained all vineyards and was used for two models (Model 1 and Model 2, see Table \ref{tab:tab1}). The second subset contained vineyards which either recorded a value for average price of sale per tonne through Sustainable Winegrowing Australia, or were within a region with an average price of sale recorded by Wine Australia; this subset was used for three further models (Models 3, 4 and 5, see Table \ref{tab:tab1}). These subsets meant that the data would be limited to samples which had recorded values for the response variables (see Table \ref{tab:tab1}), as every sample/vineyard had a recorded value for yield but not average price of sale per tonne.

@@

The second subset of data (used for Model 3, Model 4 and Model 5, see Table \ref{tab:tab1}) contained 2878 samples spanning the period from 2015 to 2022, covering 51 GI Regions and 944 separate vineyards. Average price of sale per tonne was extracted from both Wine Australia (1842 values) and Sustainable Winegrowing Australia (remaining 1036 values).

@@

We converted multiple emission sources into scope one emissions using the equation given from the Australian National Greenhouse Accounts Factors \citep{agdeeNationalGreenhouseAccounts2021}. The calculation conducted using

@@

where emissions was the the product of the quantity of fuel in litres, $Q$, a prescribed Energy Content, $EC$, and emission factors (as given by the Australian National Greenhouse Accounts factors) of scope one, $EF1$, and scope three, $EF3$, to tonnes of Carbon Dioxide Emission equivalent, $tCO2e$ \citep{departmentofclimatechangeenergytheenvironmentandwaterAustralianNationalGreenhouse2022}.

@@

\begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{my_map.pdf}}
  \caption{Map of each GI Regions average income for a vineyard of that region (average grape sale price per tonne $\times$ total tonnes yielded).}\label{fig:map}
\end{figure}%%

@@

Differences in vineyard locations were captured through the use of Geographical Indicator Regions defined by Wine Australia \citep{hallidayAustralianWineEncyclopedia2009,oliverReviewSoilPhysical2013,soarClimateDriversRed2008}. Although vineyards generally differed in income, there were pronounced differences between regions as shown in Figure \ref{fig:map}. These differences were likely due to the site of a vineyard being important as it predetermines several physical parameters such as climate, geology and soil, making location a widely considered key determinant of grape yield and average sale price \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,fragaMultivariateClusteringViticultural2017}. Each GI Region has its own unique mixture of climatic and geophysical properties that describes a unique winegrowing region within Australia and is a protected trademark under the Wine Australia act \citep{attorney-generalsdepartmentWineAustraliaCorporation2010}. Both Wine Australia and Sustainable Winegrowing Australia used the same GI Region categorical variable format to describe location.

@@

Models were validated using K-fold cross validation calculated. K-fold cross validation works by removing a subset of data from the sample used to train models and then predicts those variables to determine how sensitive the model is to changes in the sample data. For this analysis each model was validated using 10 folds, repeated 100 times.

@@

\begin{table}[]
  \caption{Summary of each Model's coefficients for continuous variables}\label{tab:contvar}
  \resizebox{\textwidth}{!}{
    \begin{tabular}{@{}cccccccc@{}}
      \begin{tabular}{@{}cccccccc@{}}
        \toprule
        \textbf{} & \textbf{} & \textbf{Intercept} & \textbf{Area Harvested} & \textbf{Water Used} & \textbf{\begin{tabular}[c]{@{}c@{}}Scope One\\ Emissions\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Area Harvested \\ ** \\ Scope One Emissions\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Area Harvested \\ ** \\ Water Used\end{tabular}} \\ \midrule
        \multirow{2}{*}{Model 1} & Coefficient & -0.0332 & 0.7418 & 0.0866 & 0.0673 &  &  \\
         & Std Error & 0.0196 & 0.0100 & 0.0089 & 0.0080 &  &  \\
         &  &  &  &  &  &  &  \\
         \multirow{2}{*}{Model 2} & Coefficient & 0.1696 & 0.5774 & 0.1079 & 0.0850 & -0.0497 & -0.0535 \\
         & Std Error & 0.0591 & 0.0148 & 0.0131 & 0.0117 & 0.0081 & 0.0084 \\
         &  &  &  &  &  &  &  \\
         \multirow{2}{*}{Model 3} & Coefficient & 0.0181 & 0.9713 & -0.0231 & -0.0070 &  &  \\
         & Std Error & 0.0130 & 0.0072 & 0.0069 & 0.0057 &  &  \\
         &  &  &  &  &  &  &  \\
         \multirow{2}{*}{Model 4} & Coefficient & 0.1450 & 0.0024 & -0.0466 & -0.0170 & 0.0115 & 0.0014 \\
         & Std Error & 0.0528 & 0.0150 & 0.0143 & 0.0118 & 0.0079 & 0.0083 \\
         &  &  &  &  &  &  &  \\
         \multirow{2}{*}{Model 5} & Coefficient & 0.1517 &  & -0.0404 & -0.0171 &  &  \\
         & Std Error & 0.0527 &  & 0.0113 & 0.0097 &  &  \\ \bottomrule
        \end{tabular}

@@

The regression coefficients for the year for each model is depicted in Figure \ref{fig:yearly}. The first year for a model's data is used as the baseline; 2012 for Model 1 and 2, and 2015 for Model 3, 4 and 5. The Adelaide Hills is used as the regional baseline with the interaction between year and region using the first year and the Adelaide Hills as the baseline. Region and year contributed, in some but not all cases, more than the other variables. However, some years are not significant, as they are not statistically different from 0, given their error. Models 4 and 5 are very similar, indicating that the exclusion of area does not greatly affect the contribution from yearly influence. Models 4 and 5 have the most prominent trends, showing an increase in yearly effects over time, with Model 3 also increasing from 2016 to 2018 but plateau afterwards. Model 1 and 2 do not show a clear trend but do drop during 2017 and 2018 after increasing in the first 3 years.
\par
\begin{figure}
  \includegraphics{yearly_plots.pdf}
  \caption{Model Coefficient values for Year, with standard error bars.}\label{fig:yearly}
  \end{figure}

@@

Regional differences by temperature and rainfall are summarised in Figure \ref{fig:spider}. The most notable difference is between vineyards within 'Hot' and 'Very Dry' regions (warm inland regions), where high average sale prices are historically low, and yield is high. Water Use changes dramatically between these regions as well, with water being a driving force for yield but not necessarily average sale price. The warmer and drier regions tend to also have larger vineyards. These regional differences are further shown in Figure \ref{fig:yield_vs_value_area}, as a ratio of vineyard area. Where, again there is a pronounced difference in 'Hot' and 'Very Dry' regions producing more per area with lower average sale prices per area than other regions.
\par
\begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{starplots.png}}
  \caption{Radar plot of climatic profile's resource use, yield and average sale price. The left reflects vineyards in different climatic temperatures. The right reflects vineyards in different rainfall climates.}\label{fig:spider}
\end{figure}

@@

There was an expected strong relationship between size and resource use, with the overall area of a vineyard and its access to resources greatly determining the upper limit of potential yield. However, size was also inversely related to the potential average sale price. Higher average sales prices were also related to high resource inputs per area instead of the overall expenditure of resources. Vineyard yields and sales price changed greatly by region and year. Even given regional and yearly changes, there was a strong connection between smaller vineyards and higher sales prices. This could have been due to more attention available when managing smaller properties.

@@

The lack of significance of scope one emissions and its contribution to models, given its F-statistics, could be indicative that other vineyard activities requiring fuel are not leading factors for a vineyards average sale price. The relationship between yield, value and area was not simply about efficiently producing the most grapes. It is possible that the relationship of scope one emissions between yield and sale price was closely tied to a vineyard's area due to requiring more fuel to address more issues over greater distances. It is difficult to discern the connection of scope one emissions directly, as fuel can be used for a broad category of activities. 

@@

There are many on-the-ground decisions that influence both sales price and yield. The decision to prioritise average sale price over quantity, is governed by complex physical and social forces, for example international market demands, disease pressures and natural disasters \citep{abadCoverCropsViticulture2021,cortezUsingDataMining2009,hallWithinseasonTemporalVariation2011,i.goodwinManagingSoilWater2009,kasimatiPredictingGrapeSugar2022,oliverReviewSoilPhysical2013,srivastavaNondestructiveSensingMethods2018}, with many of these occurrences being highlighted throughout the reports from Wine Australia over the past decade \citep{wineaustraliaNationalVintageReport2019,wineaustraliaNationalVintageReport2021,wineaustraliaNationalVintageReport2022,winemakersfederationofaustraliaNationalVintageReport2013,winemakersfederationofaustraliaNationalVintageReport2014,winemakersfederationofaustraliaNationalVintageReport2015,winemakersfederationofaustraliaNationalVintageReport2016,winemakersfederationofaustraliaNationalVintageReport2017,winemakersfederationofaustraliaNationalVintageReport2018}. However, the changes in the coefficients (see Figure \ref{fig:yearly}) are not reflective of many known occurrences, such as the 2020 bush fires, which had higher values for coefficients than prior years; During the 2020 bush fires 40,000 tonnes of grapes were lost across 18 different wine regions due to bush fires and smoke taint. In comparison to countrywide pressures such as drought, this damage made up only 3\% of the total amount of grapes for that year; although acknowledged as a considerable loss on an individual basis, it was deemed to be only a minor national concern by Wine Australia when compared to other environmental pressures such as drought \citep{wineaustraliaNationalVintageReport2020}

@@

Some regions appeared to produce grapes of lower average sale price at scale whilst others focussed on producing higher priced grapes in lower volumes. This empirical finding is consistent with Wine Australia's annual reports, which shows that some GI regions, such as the Riverland, are known for producing large amounts of lower grade (low value per tonne) grapes \citep{wineaustraliaNationalVintageReport2022,winemakersfederationofaustraliaNationalVintageReport2017}. Comparatively, other regions, such as Tasmania, only produce grapes of higher sales price but in smaller quantities. The difference in pricing per tonne between the lowest and highest regional average sales prices was almost a hundred times, showing that region had a profound influence. Some regions also had a mixture of high and low average sales price and yield such as the Yarra Valley, showing that some regions were not solely locked into chosing a focus on high yields or high average sales price. A further possibility is the existence of regional upper limits on potential sales price, or that there are diminishing returns in some regions when pursuing higher sales prices or quantity; however these types of relationships may be obfuscated by knowledgeable winegrowers who avoid such pitfalls.

@@

Due to regional differences, different strategies are  employed, such as some regions targeting mass production over higher sales price. This is most notable when grouping regions by climate, especially when considering GI Regions in the 'Hot Very Dry' climate (see Figure \ref{fig:yield_vs_value_area}). Figure \ref{fig:spider} also shows that comparatively 'Warm' and 'Dry' Regions manage their resources incredibly efficiently having generally larger areas using similar resources too those in 'Cool' regions but having areas comparable to regions in 'Hot' climates. The coefficients for Model 4 also show a greater benefit of resource use per area when producing grapes at higher average sale prices, showing higher resource use per area reflective of higher average sales price (see Table \ref{tab:summary}).
